Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-13 paper/disc20clustering.tex
comments

We start by constructing a~ground set of size $k-1$ on an arbitrarily chosen cluster.
In any partition, there must exist an isolated node collocated with the ground set of size $k-1$, and we call it \emph{special}.
We issue requests between the current special node, and some node that was initially collocated with it.
By repeating such requests, almost every node is collocated with the first ground set at some point .
In comparison, we show that there exists an optimal offline algorithm \OPT that performs only two migrations.
\mahmoud{4 migrations?}
Figure~\ref{fig:lb} illustrates the constructs used in the lower bound.

>>>>

We start by constructing a~ground set of size $k-1$ on an arbitrarily chosen cluster.
In any partition, there must exist an isolated node collocated with the ground set of size $k-1$, and we call it \emph{special}.
We issue requests between the current special node, and some node that was initially collocated with it.
By repeating such requests, almost every node is collocated with the first ground set at some point .
In comparison, we show that there exists an optimal offline algorithm \OPT that performs only two node exchanges ("swaps").
Figure~\ref{fig:lb} illustrates the constructs used in the lower bound.
